From Reversible Programs to \\ Univalent Universes and Back

### 2021-10-27 Pi/paper/introduction.tex
Citation updates

\noindent
The proofs of some of our lemmas and propositions and theorems, as well as additional material, are given in the
supplementary appendices, and we refer to them in the text. Our accompanying Agda code contains the formalisation of the
full syntax, and most of our proofs.

>>>>

\noindent
The proofs of some of our lemmas and propositions and theorems, as well as additional material, are given in the
supplementary appendices in the extended version~\cite{choudhurySymmetriesReversibleProgramming2021}, and we refer to
them in the text. Our accompanying Agda code~\cite{choudhuryArtifactSymmetriesReversible2021} contains the formalisation
of the full syntax, and most of our proofs.
